The Design and Implementation of the Synchronous Language \CEU

### 2016-10-03 paper.tex
(>) sccharts

\begin{figure}[!htb]
 \centering
 %\includegraphics[width=0.5\columnwidth]{terra}
\caption{Terra programming system basic elements.}
 \label{fig.terra}
\end{figure}

@@

Like \CEU, many synchronous languages rely on deterministic scheduling to 
preserve intra-reaction determinism (%
\emph{Reactive C}~\cite{rp.rc},                 % 1991
\emph{Protothreads}~\cite{wsn.protothreads},    % 2006
\emph{SOL}~\cite{wsn.sol},                      % 2007
\emph{SC}~\cite{rp.synchc},                     % 2009
and
\emph{PRET-C}~\cite{rp.pretc}).                 % 2010
%
%It is the responsibility of the programmer to specify the execution order for 
%threads, based on either explicit priorities, or source code lexical order 
%(similar to \CEU).
%
\CEU also performs concurrency checks to detect trails that, when reordered,
change the observable behavior of the program, i.e., trails that actually rely
on deterministic scheduling.
%
%These languages have a tick-based notion of time similar to Esterel, which 
%prevents the concurrency checks of \CEU.

>>>>

TODO:
\begin{figure}[!htb]
 \centering
 %\includegraphics[width=0.5\columnwidth]{terra}
\caption{Terra programming system basic elements.}
 \label{fig.terra}
\end{figure}

@@

Like \CEU, many synchronous languages rely on deterministic scheduling to 
preserve intra-reaction determinism (%
\emph{Reactive C}~\cite{rp.rc},                 % 1991
\emph{Protothreads}~\cite{wsn.protothreads},    % 2006
\emph{SOL}~\cite{wsn.sol},                      % 2007
\emph{SC}~\cite{rp.synchc},                     % 2009
and
\emph{PRET-C}~\cite{rp.pretc}).                 % 2010
%
%It is the responsibility of the programmer to specify the execution order for 
%threads, based on either explicit priorities, or source code lexical order 
%(similar to \CEU).
%
\CEU also performs concurrency checks to detect trails that, when reordered,
change the observable behavior of the program, i.e., trails that actually rely
on deterministic scheduling.
%
%These languages have a tick-based notion of time similar to Esterel, which 
%prevents the concurrency checks of \CEU.
\emph{SCCharts}~\cite{sccharts.1} proposes \emph{sequentially constructive
programs} that allow ``shared variables to have multiple values per tick as
long as these values are explicitly ordered by sequential
statements''~\cite{sccharts.2}.
This relaxes Esterel's restriction for \emph{read-after-write} accesses only
(e.g., a signal must be emitted to be present) and permits
\emph{write-after-read} accesses typical in imperative programs (e.g., test and
set).
Although this approach still restricts concurrent accesses, it does not impose
strict deterministic scheduling such as in \CEU.
